EvoSwarm: A Cloud-Native Architecture for the Reproducible Execution of Multi-population Optimization Algorithms

### 2020-05-18 draft.tex
Eliminates question and solves

First, we focused on knowing how scaling is related to the number of populations
and workers in the system. This experiment concludes that there is an
interesting interplay, with the most benefit obtained with a number of
populations slightly above the number of workers, which brings performance gains 
in terms of execution speed with experiments taking less time since
evaluations are shared between different workers. % of what kind? - JJ
Also, we found that for lower dimensions, there is an advantage in using fewer
populations. % Specify that.

>>>>

First, we focused on knowing how scaling is related to the number of populations
and workers in the system. This experiment concludes that there is an
interesting interplay, with the most benefit obtained with a number of
populations slightly above the number of workers, which brings performance gains 
in terms of execution speed with experiments taking less time since
evaluations are performed simultaneously by different workers.
Also, we found that for lower dimensions, there is an advantage in using fewer
populations. % Specify that.
